Article Title

### 2013-08-15 sections/Theory.tex
edited the Theory section

\emph{Regularization} is the deliberate biasing of the unbiased estimate toward a less variable low-dimensional \emph{target estimate} $\hat T$ in order to minimize the estimator risk by striking a favorable balance between bias and variance.
A regularized covariance matrix estimator must solve two problems: (a) choose and fit the target covariate estimate $\hat T$ and (b) mix $\hat\Sigma_0$ with $\hat T$ by the optimal amount. 
Regularized covariance matrix estimates can be generally expressed as 
\begin{equation}
\hat\Sigma_{d,\lambda} = mix(\Sigma_0,\hat T_{\hat d},\hat\lambda) 
\end{equation}
where $\hat d$ indicates the choice of the target estimate from the family of target estimates $\hat T_d$. $mix(\cdot,\cdot,\hat\lambda)$ is the mixing function of $\hat\Sigma_0$ and $\hat T_{\hat d}$ in proportion controlled by $\hat \lambda$. Both $\hat d$ and $\hat \lambda$ must be calculated from the training sample.

A number of regularization schemes have been developed, which differ by their target estimates and mixing functions.  In this study, we evaluate four regularized estimators.

@@

A regularized estimate requires the following three choices: 
\begin{enumerate}[  1. ]
\item define a set of low-dimensional target estimates
\item given the data, select the optimal target estimate from the set 
\item given the data, select the optimal amount of biasing toward the target estimate
\end{enumerate}
The first choice, the selection of the general form of target estimates, must be made \emph{a priori}.  Curiously, \emph{some} improvement can be produced with an arbitrary target estimate as long as its variance is lower than that of the unbiased estimator.  The perplexing fact that estimates can be improved by a bias toward an arbitrary less variable target is known as \emph{Stein's paradox} \citep{Efron:1977}.

@@

Regularization is the game of minimizing risk $r_\gamma$ by reducing estimation error $\varepsilon_\gamma$ at the cost of increased bias $b_\gamma$, the \emph{bias-variance tradeoff}.  \TODO{This point can be untuitive.  For example, \cite{Varoquaux:2012} misrepresents the effect of regularization by stating that regularization removes the upward bias of correlations in the sample covariance matrix. In reality, regularization should start with an unbiased estimator and bias it toward a low-variance target so that the estimation risk is reduced. Another important point is ``Stein's paradox'': regularization does not improve the estimate of each covariance. In fact, it makes it worse. Regularization only improves the risk when measured on the entire matrix. Regularization should not be used to improve the estimate of average correlations or the distribution of correlations.}
We follow the convention that $\hat\Sigma_{\gamma=0}$ is the unbiased estimator $\hat\Sigma_0$, \emph{i.e.}\;$b_{\gamma=0}^2 = 0$. 
We define a sequence of approximations $\hat\Sigma_\gamma$ that become less variable as as $\gamma$ increases, which is usually accompanies by increased bias. Then $\hat\Sigma_\gamma$ defines the \emph{regularization path}, for which \emph{regularization intensity} $\gamma$ specifies the location along the path, which may be real-valued or discrete, or even a vector to steer the bias toward multiple targets.

\paragraph{Evaluation of estimators:}

@@

\paragraph{Our choices of regularized covariance estimates:}
\begin{enumerate}[\qquad 1.\;\;]
\item sample covariance (benchmark)
\item linear shrinkage toward identity 
\item linear shrinkage toward a single-factor model.
\item multifactor
\item graphical lasso
\item latent-variable graphical lasso
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/Figure2.pdf}
\caption{
%\textbf{Figure 2.}{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: In the Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from sparse pairwise linear interactions between visible units. 
\textbf{D}: In the Gaussian graphical model with latent units, correlations arise  between pairs of nodes 
}\label{fig:02}
%}
\end{figure}

>>>>

\emph{Regularization} is the deliberate biasing (`shrinkage') of the unbiased estimate toward a less variable low-dimensional \emph{target estimate} $\hat T$ in order to minimize the estimator risk by striking a favorable balance between bias and variance.
A regularized covariance matrix estimator must solve two problems: (a) choose and fit the target covariate estimate $\hat T$ and (b) mix $\hat\Sigma_0$ with $\hat T$ by the optimal amount. 
Regularized covariance matrix estimates can be generally expressed as 
\begin{equation}
\hat\Sigma_{d,\lambda} = mix(\Sigma_0,\hat T_{\hat d},\hat\lambda) 
\end{equation}
where $\hat d$ indicates the choice of the target estimate from the family of target estimates $\hat T_d$. $mix(\cdot,\cdot,\hat\lambda)$ is the mixing function of $\hat\Sigma_0$ and $\hat T_{\hat d}$ in proportion controlled by $\hat \lambda$. Both $\hat d$ and $\hat \lambda$ must be calculated from the training sample.

A number of regularization schemes have been developed, which differ by their target estimates and mixing functions.    Curiously, \emph{some} improvement can be produced with an arbitrary target estimate as long as its variance is lower than that of $\hat\Sigma_0$.  The perplexing phenomenon that estimates can be improved by a bias toward an arbitrary less variable target is known as \emph{Stein's paradox} \citep{Efron:1977}.   \TODO{This point can be untuitive.  For example, \cite{Varoquaux:2012} misrepresents the effect of regularization by stating that regularization removes the upward bias of correlations in the sample covariance matrix. In reality, regularization should start with an unbiased estimator and bias it toward a low-variance target so that the estimation risk is reduced.} However, if a family of target estimates can capture the underlying regularities in the covariance structure of a specific system with a small number of parameters, biasing the estimate toward these targets ought to produce a greater reduction in estimator risk.

In this study, we evaluate four regularized estimators whose target estimates correspond to the graphical models in Figure \ref{fig:02}: diagonal (A), multifactor (B), sparse partial correlations (C), and sparse  partial correlations with latent units (D).  The following describe each regularization scheme separately.

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/Figure2.pdf}
\caption{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: In the Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from sparse pairwise linear interactions between visible units. 
\textbf{D}: In the Gaussian graphical model with latent units, correlations arise  between pairs of nodes 
}\label{fig:02}
\end{figure}

\subsection{Estimator A: Shrinkage toward a diagonal}
The most popular covariance regularization schemes use diagonal target estimates and linear shrinkage toward the target.  For example, the target could be the identity matrix:  
\begin{equation}
\hat T = \hat v I
\end{equation}
where $\hat v = \frac 1 p \sum\limits_{i=1}^p(\hat\Sigma_0)_{ii}$ is the mean sample variance.

Alternatively, the target could contain the sample variances:
\begin{equation}
\hat T= \hat\Sigma_0 \circ I 
\end{equation}
where $\circ$ is the entrywise matrix product.

Finally, the target could be a linear mixture of the common variance and independent variance targets
\begin{equation}
\hat T_\eta = (1-\eta)(\hat\Sigma_0 \circ I) + \eta\hat v I
\end{equation}

The regularized estimator is the linear mixture of $\hat\Sigma_0$ and $\hat T_\eta$:
\begin{equation}
\hat\Sigma_{\eta,\lambda} = (1-\lambda)\hat\Sigma_0 + \lambda \hat T_\eta 
\end{equation}

\subsection{Estimator B: Shrinkage toward a factor model}

\subsection{Estimator C: Sparse partial correlations}

\subsection{Estimator D: Sparse partial correlations with latent units}

@@

A regularized estimate requires the following three choices: 
\begin{enumerate}[  1. ]
\item define a set of low-dimensional target estimates
\item given the data, select the optimal target estimate from the set 
\item given the data, select the optimal amount of biasing toward the target estimate
\end{enumerate}

@@

Regularization is the game of minimizing risk $r_\gamma$ by reducing estimation error $\varepsilon_\gamma$ at the cost of increased bias $b_\gamma$, the \emph{bias-variance tradeoff}.  
We follow the convention that $\hat\Sigma_{\gamma=0}$ is the unbiased estimator $\hat\Sigma_0$, \emph{i.e.}\;$b_{\gamma=0}^2 = 0$. 
We define a sequence of approximations $\hat\Sigma_\gamma$ that become less variable as as $\gamma$ increases, which is usually accompanies by increased bias. Then $\hat\Sigma_\gamma$ defines the \emph{regularization path}, for which \emph{regularization intensity} $\gamma$ specifies the location along the path, which may be real-valued or discrete, or even a vector to steer the bias toward multiple targets.

@@
